Examining Whether Approximate Visualizations Impact Perception of Corrected Visualizations

### 2016-12-12 paper/paper.tex
remove redundant participants section

\subsubsection{Participants}

We recruited 34 participants from Amazon Mechanical Turk (AMT), a common tool to run perception studies for visualizations~\cite{heer2010crowdsourcing}.
Similar to other studies of human perception of visualizations, we restricted participation to people on AMT with at least 1,000 tasks completed and an approval rate above 95\%.
Participation was restricted to the United States to ensure familiarity with the airlines and states in the dataset.
Participants were compensated \$2.00 for completing the study.

@@

@@

\begin{table}[!t]
% increase table row spacing, adjust to taste
\renewcommand{\arraystretch}{1.3}
% if using array.sty, it might be a good idea to tweak the value of
% \extrarowheight as needed to properly center the text within the cells
\caption{The errors for different questions. The results in parentheses are with outliers removed (sigma clipping with $4 \time sigma$).}
\label{table_errors}
\centering
\begin{tabular}{|l||r|r|r|r|}
\hline
Question & Data        & Mean error & Standard deviation \\ \hline
\hline
type 1   & approx      & 0.117 (0.021)     & 0.535 (0.035)             \\ \hline
type 1   & precise     & 0.099 (0.087)     & 0.167 (0.130)            \\ \hline
type 2   & approx      & 0.803 (0.420)     & 1.649 (0.528)            \\ \hline
type 2   & precise     & 2.075 (0.469)     & 8.500 (0.453)            \\ \hline
\end{tabular}
\end{table}

>>>>

@@

We recruited participants from Amazon Mechanical Turk (AMT), a common tool to run perception studies for visualizations~\cite{heer2010crowdsourcing}.
Similar to other studies of human perception of visualizations, we restricted participation to people on AMT with at least 1,000 tasks completed and an approval rate above 95\%.
Participation was restricted to the United States to ensure familiarity with the airlines and states in the dataset.
Participants were compensated \$2.00 for completing the study.

@@

\begin{table}[!t]
% increase table row spacing, adjust to taste
\renewcommand{\arraystretch}{1.3}
% if using array.sty, it might be a good idea to tweak the value of
% \extrarowheight as needed to properly center the text within the cells
\caption{The errors for different questions. The results in parentheses are with outliers removed (sigma clipping with $4 \times sigma$).}
\label{table_errors}
\centering
\begin{tabular}{|l||r|r|r|r|}
\hline
Question & Data        & Mean error & Standard deviation \\ \hline
\hline
type 1   & approx      & 0.117 (0.021)     & 0.535 (0.035)             \\ \hline
type 1   & precise     & 0.099 (0.087)     & 0.167 (0.130)            \\ \hline
type 2   & approx      & 0.803 (0.420)     & 1.649 (0.528)            \\ \hline
type 2   & precise     & 2.075 (0.469)     & 8.500 (0.453)            \\ \hline
\end{tabular}
\end{table}
